Textbook Knowledge on Hospital Information Management as Linked Data

### 2019-09-17 paper.tex
Add snik references to bibliography.
Extend application.

\section{Application}\label{sec:application}
SNIK was initially intended~\citep{domaene} as the data source for software to support hospital CIOs.
Two applications were designed and implemented as prototypes: (1) the requirements engineering decision support system TOREOnto~\citep{toreonto} and (2) the knowledge exploration and navigation visualization CIONo~\citep{ciono}.\todo{add ciono to bib}
Due to data protection regulations, efforts to integrated them into the informational infrastructure of the Uniklinikum Leipzig were stopped.
Subsequent efforts shifted to ontology assisted teaching.

@@

SNIK Graph~\citep{snikgraph} is a web application\footnote{\url{http://www.snik.eu/graph}} that transforms the classes and triples of SNIK to nodes and edges of a graph.
The graph is visualized using the Cytoscape.js~\citep{cytoscape} library with the spring-based Euler layout\todo{cite?}.
The u~\cref{fig:snik-graph-overview}

@@

\section{Acknowledgments}
This work is supported by the DFG (German Research Foundation) under the Projects SNIK, grant no. 1605/7-1 and 1387/8-1, as well as HITO, grant no. WI 1605/11-1 and I3726-N31.
%We thank the publishers ... and ... for granting us permission to publish the subontologies based on the textbooks \citet{bb,ob,he} under an open license.
%\nocite{*} 
\bibliographystyle{ios1}
\bibliography{paper}

>>>>

\section{Application}\label{sec:application}
SNIK was initially intended~\citep{domaene} both as the data source for software to support hospital CIOs and to support teaching.
For the former goal, two applications were designed and implemented as prototypes~\citep{toreonto}: (1) the requirements engineering decision support system TOREOnto and (2) the knowledge exploration and navigation visualization CIONx.
Due to internal regulations, efforts to integrate them into the informational infrastructure of the Uniklinikum Leipzig were stopped.
Consequently, latter efforts concentrate on the teaching support:

@@

SNIK Graph is a web application\footnote{\url{http://www.snik.eu/graph}} that transforms the classes and triples of SNIK to nodes and edges of a graph.
The graph is visualized using the Cytoscape.js~\citep{cytoscape} library with the force-directed Euler layout.
The u~\cref{fig:snik-graph-overview}

@@

\section{Acknowledgments}
This work is supported by the DFG (German Research Foundation) under the Projects SNIK, grant no. 1605/7-1 and 1387/8-1, as well as HITO, grant no. WI 1605/11-1 and I3726-N31.
%We thank the publishers ... and ... for granting us permission to publish the subontologies based on the textbooks \citet{bb,ob,he} under an open license.
%\nocite{*} 
\bibliographystyle{ios1}
\bibliography{paper,snik}
